---
title: "lab_state_income"
output: html_notebook
---

Question 1.

## Load in the data, and have a look at it. How many variables does it have? How many observations? What are the variable names? What type of variables does it have?

```{r}

state_income_data <- read_csv("/Users/kahlen/Desktop/CodeClan/Codeclan_work/week_01/day_2/week1_day2/data/state_income_data.csv")

str(state_income_data)

```


Question 2.

Select the columns which contain the information from years 2002 to 2008. Ensure you keep the Index and State variables as well.

```{r}

get_years <- state_income_data %>% 
  select(1:9)
get_years
```


Question 3.

Rename the Index column to first_letter. Hint: look up the rename() function.

```{r}

state_income_data2 <- rename(state_income_data, first_letter = Index)
state_income_data2
```


Question 4.

Find the seven states which start with an A,B, or C.

```{r}

seven_states <- filter(state_income_data2, first_letter %in% c("A","B","C"))
seven_states
```


Question 5.

Find which of these seven states have the greatest income in 2008.

```{r}
arrange(seven_states, desc(Y2008))
```


Question 6.

Calculate the change in income for each state of these seven states (states starting with A,B, or C) between 2002 and 2008. Save the income change in a new column called income_change.

```{r}

seven_states <- mutate(seven_states, income_change = Y2008 - Y2002, .before = 3)
seven_states
```


Question 7.

Find which of these seven states income change is greater than 500,000 (i.e. an increase of 500,000 or decrease of 500,000).

```{r}

filter(seven_states, income_change > 500000)

```


Question 8.

Calculate the mean and median income change for all seven states.

```{r}
summary(seven_states)
```


Question 9.

Go back to the original dataset which contains all states. Write a pipe which selects the State and Y2008 variables, arranges the income from highest to lowest, filters all those states which have a income of greater than 1 million, and then finally chooses the top 10 wealthiest states.

```{r}


state_income_data2 %>% 
  select(State,Y2008) %>% 
  arrange(desc(Y2008)) %>% 
  filter(Y2008 > 1000000) %>% 
  head(10)

```

