---
title: "week_6_day_2_distributions_homework"
output: html_notebook
---

##Q1. 
Load the data
```{r}

library(tidyverse)
library(janitor)

items <- read_csv(here::here("data/20190928-items.csv"))

items <- items %>% 
  clean_names()
  

head(items)

```

##Q2. 
Find the brand with the highest numbers of phones in the dataset.
```{r}

  items_count <- items %>% 
  group_by(brand) %>% 
  count(brand)

#Samsung has the highest numbers of phones in the dataset

```


##Q3. 
Plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. 
```{r}

rating_stats <- items %>% 
  filter(brand == "Samsung") %>% 
  summarise(
    num = n(),
    mean = mean(rating),
    sd = sd(rating)
  )
  
rating_stats

```
```{r}


items %>% 
  filter(brand == "Samsung") %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", bins = 25)+
  stat_function(
    fun = dnorm,
    args = list(
      mean = rating_stats$mean,
      sd = rating_stats$sd
    ),
    col = "red"
  )


```

## Q4 
You calculated the mean() and sd() of your distribution in an earlier question. 
Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.

```{r}

items_samsung <- items %>% 
  filter(brand == "Samsung")

items_samsung %>%
  filter(rating >= rating_stats$mean - rating_stats$sd) %>%
  filter(rating <= rating_stats$mean + rating_stats$sd) %>%
  summarise(prop_within_1sd = n() / nrow(items_samsung))


items_samsung %>%
  filter(rating `` rating_stats$mean - rating_stats$sd) %>%
  filter(rating `` rating_stats$mean + rating_stats$sd) %>%
  summarise(prop_within_2sd = n() / nrow(items_samsung))

items_samsung %>%
  filter(rating `` rating_stats$mean - rating_stats$sd) %>%
  filter(rating `` rating_stats$mean + rating_stats$sd) %>%
  summarise(prop_within_3sd = n() / nrow(items_samsung))



```

```{r}

items_samsung %>% 
  group_by(brand) %>% 
  summarise(
    Q1 = quantile(rating, 0.25),
    Q2 = quantile(rating, 0.5),
    Q3 = quantile(rating, 0.75),
    IQR = Q3 - Q1
  )


```






