---
title: "R Notebook"
output: html_notebook
---


Q1. Load in data
```{r}

library(tidyverse)
library(janitor)
library(ggplot2)

ames <- read_csv(here::here("data/ames.csv")) %>% 
  clean_names()

```

Q2. Investigate the distribution of lot_area

```{r}

ames %>% 
  ggplot(aes(x = lot_area))+
  geom_histogram(col = "white", fill = "steel blue", alpha = 0.7)+
  
  #The distribution is not normal. It does not show the modal clearly since the range is very large, only observations that are below 50,000 is considered in this graph.
```

Q.3 Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.

```{r}

library(infer)

ames_resample_200 <- ames %>% 
  rep_sample_n(size = 200, replace = TRUE, reps = 5000) %>% 
  summarise(
    mean_lot_area = mean(lot_area)
  )

ames_resample_200
  

ames_resample_200 %>% 
  ggplot(aes(x = mean_lot_area))+
  geom_histogram(col = "white", fill = "steel blue", alpha = 0.7)
  

```
Q4. Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution

```{r}

ames_resample <- ames%>% 
  specify(response = lot_area) %>% 
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "mean")

ames_resample_ci_95 <- ames_resample%>% 
  get_confidence_interval(level = 0.95, type = "percentile")

ames_resample_ci_95

ames_resample %>% 
  visualise(bins = 30) +
  shade_confidence_interval(endpoints = ames_resample_ci_95)

```

Q.5 You would like to know the mean(lot_area) of the sold houses with higher confidence. 
Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). 
Is it narrower or broader than the 95% CI? Does that make sense?

```{r}

 ames_resample_ci_99 <- ames_resample %>% 
  get_confidence_interval(level = 0.99, type = "percentile")


ames_resample %>% 
  visualise(bins = 30) +
  shade_confidence_interval(endpoints = ames_resample_ci_99)


#It does make sense that ci 99% is broader than ci 95%

```

Q6. Calculate the point estimate of the mean(lot_area)
```{r}


ames_resample_200 %>%
  summarise(point_est = mean(mean_lot_area))


```

