---
title: "Week1_Weekend_Homework_by_Kahlen_Cheung"
output: html_notebook
---

# Introduction

This R excercise adpots functions from the package `tyidyverse` and `janitor`. The excercise focuses on the usage of data cleaning such as recoding and dealing with missing data. The dataset `book` is scraped from `Goodreads`, which is publicy available on [Kaggle](https://www.kaggle.com/jealousleopard/goodreadsbooks).

## Preparartion
Import data and inspect data structure
```{r}

book <- read_csv("/Users/kahlen/Desktop/CodeClan/codeclan_homework_KahlenCheung/week_01/day_5/data/books.csv")
glimpse(book)
drop_na(book)
view(book)

# Change the type of `publication_date` from chr to date(dbl) for better processing
    
publication_date_adjusted <- book %>% 
  group_by(publication_date)%>% 
  mutate(publication_date = as.Date(publication_date, "%m/%d/%y"))

glimpse(publication_date_adjusted)

view(publication_date_adjusted)

typeof(publication_date_adjusted$publication_date)

# time cost :1hr 50mins; 1hr on figuring how to change the type of date (or change the type of column in a data frame)

#as.Date(head(book$publication_date), "%m/%d/%y"
#lubridate::(publication_date_adjusted$publication_date)

```

## Explore data insights-creating subsets
-create a subset by selecting useful columns

```{r}

book_subset <- publication_date_adjusted %>% 
  select("title", "authors", "average_rating", "ratings_count", "text_reviews_count", "publication_date", "publisher")

view(book_subset)


#book's average rating and filter rows ratings_count less than 10,000 

book_rarting <- book_subset %>% 
 filter(ratings_count >= 10000, .preserve = FALSE) %>%  
 select(average_rating, title) %>% 
 arrange(desc(average_rating))

book_rarting

book_rarting%>% 
head(5)

#The top 5 books(items) that have the most average rating where the number of rating counts are equal to or more than 10,000:
#The Complete Calvin and Hobbes, Harry Potter Boxed Set Books 1-5 (Harry Potter #1-5), It's a Magical World (Calvin and Hobbes #11), Harry Potter Collection (Harry Potter #1-6), Homicidal Psycho Jungle Cat (Calvin and Hobbes #9)

book_rarting%>% 
tail(5)

#The 5 books(items) that have the least average rating where the number of rating counts are equal to or more than 10,000:
#The Mermaid Chair, Billy Budd Sailor, The Jane Austen Book Club, Four Blondes, Lost

```

```{r}

                                   
book_rarting %>% 
  select(average_rating)%>% 
  mutate(level_of_ratings = case_when(
                                   as.numeric(average_rating * 100) >= 420 ~ "Execellent", 
                                   as.numeric(average_rating * 100) >= 320 ~ "Good",
                                   as.numeric(average_rating * 100) >= 280 ~ "Fair"),
                                   .before = 3)
      
    
#the average_rating column was `double` format, times 100 to avoid decimal calculation and classification. 
#In this case it can't be a `int` type since it will go rather upward or downward that
#the result will be inaccurate.

#wrong example:
# 
# book_rating %>% 
#   as.numeric(average_rating) %>% 
#   select(average_rating)%>% 
#   mutate(level_of_ratings = case_when(
#                                    average_rating >=4.2 ~ "Execellent", 
#                                    average_rating >=3.2 && average_rating <4.2 ~ "Good",
#                                    average_rating >=2 && average_rating <3.2 ~ "Fair"),
#                                    .before = 3)

tail(book_rarting)
                                    
```

```{r}

#Find out how many items were published in 2019 and 2020


book_subset %>% 
  group_by(publication_date) %>% 
  mutate(year_of_publish = select(publication_date, contains("2020") | select(publication_date)))
                          


book_subset %>% 
  count(publication_date, "2020") 

# 724 items were released in 2020


book_subset %>% 
  select(publication_date == startsWith("2020"))
         
sum

# book_subset %>% 
#   group_by(publication_date) %>% 
#   mutate(year_of_publish = 
#            recode(contains(publication_date, "2020") == "2020",
#                   contains(publication_date, "2019") == "2019"))


#tried to use `startsWith` / `contains` to distinct the years ;



```

```{r}

# library(stringr)

funny_thing <- c('e')

book %>% 
  count(authors, sort = TRUE)

book %>% 
cor(ratings_count)

ggplot(books,aes(average_ratings, log10(num_pages), colour = publisher))

```

```{r}

#class review

#books %>% 
# count(language_code) %>% 
#   filter(n == 1) %>% 
#   pull(language_code)

book %>% 
  select.list(language_code) %>% 
  group_by(language_code) %>% 
  summaraize(n=N())
#n tells how many rows there are

# if_else((books$language_code =="en-GB, TRUE, FALSE"))
# books$language_code == "en-GB

"


```

