---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
```


```{r}

customers <- read_csv(here::here("data/mall_customers.csv")) %>% 
  clean_names() %>% 
  rename(annual_income = annual_income_k) %>% 
  rename(spending_score = spending_score_1_100) %>% 
  select(-customer_id) %>% 
  na.omit()

customers 

```

## Exploring Data

(is is suitable for clustering)

```{r}

customers %>% 
  ggplot(aes( spending_score, annual_income, colour = gender))+
  geom_point()


```

```{r}

customers %>% 
  ggplot(aes(spending_score))+
  geom_histogram()
 

```


```{r}

customers %>% 
  ggplot(aes(annual_income))+
  geom_histogram()

```


## K-means clustering

```{r}

 customers_data <- customers %>% 
  select(spending_score, annual_income)

```


```{r}


 customers_data %>% 
  as_tibble() %>% 
  pivot_longer(cols = c(spending_score, annual_income),
               names_to = "type",
               values_to = "value") %>% 
  group_by(type) %>% 
  summarise(mean = round(mean(value)),
            sd = sd (value))

```
* the mean and sd of `annual_income` and `spending_score` is pretty close. Scaling is unnecssary is this case.

```{r}

# customers_scale <- customers %>% 
#   mutate_if(is.numeric, scale)

```


```{r}

customers_clustered <- kmeans(customers_data,
                              centers = 5,
                              nstart = 20)

customers_clustered 
``` 

```{r}

library(broom)

tidy(customers_clustered,
     col.names = colnames(customers_data))

```

```{r}

glance(customers_clustered)

```


### Set min & max number of cluster


```{r}

max_k <- 15

k_customers_clusters <- tibble(k = 1 : max_k) %>% 
  mutate(kclust = map(k, ~kmeans(customers_data, .x, nstart = 20)),
         tidied = map(kclust, tidy),
         glanced = map(kclust, glance),
         augmented = map(kclust, augment, customers_data))

k_customers_clusters 

```


```{r}

clustering <- k_customers_clusters %>% 
  unnest(glanced)

clustering 

```


### Choose the number of cluster (k = ...)

* Perform ggplot to visualise the results

```{r}

ggplot(clustering, aes(x = k, y = tot.withinss))+
  geom_point()+
  geom_line()+
  scale_x_continuous(breaks = seq(1, 15, by = 1))

```


* Use `fviz_nbclust` to find a suitable number of cluster

```{r}
library(factoextra)
```

To find optimal number of clusters

_Elbow method_

```{r}

fviz_nbclust(customers_data,
             kmeans,
             method = "wss",
             nstart = 20)

```

* In this graph it shows that there is a slight change of rate at around k =3, which means it suggests that the optimal number of clusters for this dataset is 3.

_Silhouette coefficient_



```{r}

fviz_nbclust(customers_data,
             kmeans,
             method = "silhouette",
             nstart = 20)

```

* A value of k = 5 is the maximum, with points also close to the average silhouette width of 0.5. Still, we ideally looking for a higher value.

_Gap Statistics_

```{r}

fviz_nbclust(customers_data,
             kmeans,
             method = "gap_stat",
             nstart = 20,
             k.max = 15)


```

(k = 1 is local maixmum, no need to use it;
k = 5 is global maximum, choose it in this case)

(highlight the one before the peak)

the k = 1 is local maximum, but we won't use it 

* The null distribution of the data is generated. The k = 1 interprets the difference of a simulated null distributed data and the well clustered data. Since k =1 is the highest of local, we choose k = 2 as number for clusters.

## Conclusion

The methods suggest suggest 3 numbers for clusters: k =2, k =3, k =5

```{r}

 clustering %>% 
  unnest(cols = c(augmented)) %>%
  filter(k == 2) %>%
  ggplot(aes(x = annual_income, y = spending_score)) +
  geom_point(aes(color = .cluster))

```

The result turns out quite similar to the plot that created at the begining. 

However there is not a clear classification of two clusters:

* try k = 3


```{r}

 clustering %>% 
  unnest(cols = c(augmented)) %>%
  filter(k == 3) %>%
  ggplot(aes(x = annual_income, y = spending_score)) +
  geom_point(aes(color = .cluster))



```

It shows that cluster 1 may have more elements that worth to discover.


```{r}

clustering %>% 
  unnest(cols = c(augmented)) %>%
  filter(k == 5) %>%
  ggplot(aes(x = annual_income, y = spending_score)) +
  geom_point(aes(color = .cluster))

```



/Failed to make `gender` as column_to_rownames since it is duplicated. /

