---
title: "Text_mining_hw"
output:
  html_document:
    toc: yes
    toc_float: true
    theme: united

---
Kahlen Cheung
20/05/2022

## Load in Data

```{r}

library(tidytext)
library(tidyverse)
library(janeaustenr)

austen_books <- austen_books()

austen_books

```


## Find the most common words in both Pride & Prejudice and Sense & Sensibility.

The most common word in Pride & Prejudice & Sense & Sensibility is `the`, with a count of 8436, whereas without stopwords is `elinor`, with a count of 623

```{r}


titles <- c("Pride and Prejudice", "Sense and Sensibility")

pride_sense_book <- list(prideprejudice, sensesensibility) %>% 
  purrr::map_chr(paste, collapse = " ")

pride_sense_book_df <- tibble(
  title = titles,
  text = pride_sense_book ) %>% 
  unnest_tokens(word, text) %>% 
  group_by(word) %>%
  count(word) %>%
  arrange(desc(n))

pride_sense_book_df


pride_sense_book_null <- tibble(
  title = titles,
  text = pride_sense_book ) %>% 
  unnest_tokens(word, text) %>% 
  group_by(word) %>% 
  anti_join(stop_words) %>% 
  count(word, sort = TRUE) %>% 
  arrange(desc(n)) 

pride_sense_book_null

```

```{r}

# sense_book <- tibble(
#   id = 1: length(sensesensibility),
#   text = sensesensibility) %>% 
#   unnest_tokens(word, text) %>% 
#   group_by(word) %>% 
#   count(word) %>% 
#   arrange(desc(n)) 
# 
# sense_book 
# 
# sense_book_null <- tibble(
#   id = 1: length(sensesensibility),
#   text = sensesensibility) %>% 
#   unnest_tokens(word, text) %>% 
#   anti_join(stop_words) %>% 
#   count(word, sort = TRUE) %>% 
#   arrange(desc(n)) 
# 
# sense_book_null 

```


## Find the most common sentiment words in both Pride & Prejudice and Sense & Sensibility.
The most common sentiment words from two books is `miss`, followed by `happy` and `love`.

```{r}

pride_sense_book_null %>% 
  inner_join(get_sentiments("afinn"), by = "word") %>% 
   left_join(get_sentiments("bing"), by = "word") %>% 
  na.omit()
 
```


## Create a plot which visualises the differences between the books  

```{r}

library(ggwordcloud)

set.seed(42)
ggplot(pride_sense_book_null, aes(label = word, size = n))+
  geom_text_wordcloud()+
  geom_text_wordcloud_area(rm_outside = TRUE)+
  scale_size_area(max_size = 20)+
  theme_minimal()


```

