---
title: "R Notebook"
output: html_notebook
---

```{r}

library(tidyverse)

project_management <- read_csv(here::here("data/project_management.csv"))

```

Plot the data, taking estimated_length as the independent variable and actual_length as the dependent variable.

* Since y increases while x increases, we can know that this is a positive correlation

```{r}

project_management %>% 
  ggplot(aes(x = estimated_length, y = actual_length))+
  geom_point()

```

Calculate the correlation coefficient of estimated_length and actual_length and interpret the value you obtain.

* These variables are very strongly positively correlated.

```{r}

project_management %>% 
  summarise(cor(estimated_length, actual_length))

```

Perform a simple linear regression using actual_length as the dependent variable, and estimated_length as the independent variable. Save the model object to a variable.

```{r}

project_management_regression <- project_management %>% 
  ggplot(aes(x = estimated_length, y = actual_length))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)

project_management_regression

```

Interpret the regression coefficient of estimated_length (i.e. slope, gradient) you obtain from the model. How do you interpret the r2 value reported by the model?

```{r}

get_line <- function(x, b0, b1){
return(b0 + x * b1)
}


```



