---
title: "Week1_weekend_hm_Create functions practice"
output: html_notebook
---


```{r}

library(dplyr)
library(stringr)

```


# `if` statement and funcions

2.2.1 Write a function which multiples all numbers by 15 and adds 4.

```{r}

multiply_15_add4 <- function(x){  #remember to add {}
  x*15+4
}

#write `return(x)` will return x only(no calculation); or assign a vector name to return

multiply_15_add4(1:3)

```

2.2.2 Write a function that returns “bird”, if the input is “goose”, “duck” or “pigeon”, and returns “not bird” for all other input.

```{r}

find_bird <- function(x){
  
  ifelse( x == "goose", "bird", "not bird")
  
}

vector_for_bird <- c("goose", "apple", 5, "seagull")  #use a vector to run all objects

find_bird(vector_for_bird)

```

2.2.3 Write a function which multiplies all numbers by 10. If the input isn’t a number, the function should return “Invalid input”.

```{r}

multiply_10 <- function(num){
  
  ifelse(is.numeric(num), num*10, "Invalid input")  #first to check if the object if is numeric, then do the cacculation
  
}   #ifelse(is.numeric(num*10), num*10, "Invalid") wrong, should not check the formula's type at the beginning 

vector_multiply_10 <- c(2, 5.3, "x", 7)

multiply_10("happy")

```


# ifelse(), recode() and case_when()

2.3.1 For the vector below, make a new vector which is equal to “Big” every time the element of sizes is greater than 10, and equal to “Small” every time the element of sizes is less than or equal to 10.

```{r}

sizes <- c(13, 15, 10, 8, 22)

case_when(
  sizes > 10 ~ "Big",
  sizes <= 10 ~"Small"
)



```

2.3.2 covert the vector

apple → alpaca

banana → bonobo

cherry → chipmunk

```{r}

fruit <- c("apple", "apple", "banana", "cherry", "cherry")

str_to_title(fruit)


```

2.3.3 

The two vectors below show the ages at marriage of each member of a couple. The first elements of each vector correspond to the first couple, the second elements to the second couple, and so on.

Create a new vector which is equal to:

“Wife older” whenever the wife’s age is highest 
“Husband older” when the husband’s age is highest 
“Same age” when they are the same age

```{r}

wife_age <- c(29L, 30L, 36L, 31L, 22L)
husband_age <- c(28L, 35L, 32L, 31L, 29L)


age_of_both_sexs <- case_when(
  
  wife_age > husband_age ~ "Wife older",
  husband_age > wife_age ~ "Husband older",
  wife_age == husband_age ~ "Same age"
  
)

age_of_both_sexs


```


# Loops

2.4.1 Use a loop to print out every element of my_list which is of type character. Decide if you need a for loop or a while loop.

```{r}

my_list <- list(
  4,
  "apple",
  10.5,
  c("is", "an", "apple"),
  "apple",
  c("i", "like", "apples"),
  8
)

 for( i in my_list){
   if(is.character(i)){
     print(i)
   }
 }

```


2.4.2

Once again write a loop that prints out character elements. This time if the element has a length() greater than one, paste() all the elements in that vector together into one big character vector.

```{r}


 for(i in my_list){
   if(length(i) > 1){
     print(paste(i, collapse = " ")) #sep=" " is not for vector; use collapse = " " when it's vector
   }
 }

str_c("i", "like", "apple", sep = " ")

```


















