---
title: "R Notebook"
output: html_notebook
---

```{r}

library(tidyverse)
library(fastDummies)
library(janitor)


```

```{r}

housing_prices <- read_csv(here::here("data/housing_prices.csv")) %>% 
  clean_names()

view(housing_prices)

housing_prices %>% 
  summarise(sum_na = sum(is.na(.) == TRUE))

housing_prices <- housing_prices %>% 
  mutate(across(where(is.numeric),
                      ~coalesce(., median(., na.rm = TRUE))))
```

2. We expect the total_rooms of houses to be strongly correlated with total_bedrooms. Use ggpairs() to investigate correlations between these two variables.

The significant correaltion between total room and total bedroom is 0.931, which means highly correlated.

```{r}

library(GGally)

housing_prices_trim <- housing_prices %>% 
  select(total_rooms, total_bedrooms)


```

3. So, we do find significant correlations. Let’s drop total_bedrooms from the dataset, and use only total_rooms going forward.

```{r}

housing_prices_drop <- housing_prices_trim %>% 
  select(total_rooms)

ggpairs(housing_prices_drop)

```

4. We are interested in developing a regression model for the median_house_value of a house in terms of the possible predictor variables in the dataset.

The protentails predictors variables would be `total_rooms`, `populatpion` and `ocean_proximity`.

```{r}

median_hs_prices_sub <- housing_prices %>% 
  select(-longitude, -latitude, -total_bedrooms)

alias(lm(median_house_value ~., data = median_hs_prices_sub))

ggpairs(median_hs_prices_sub)
  

```

Perform further ggplot visualisations of any significant correlations you find.

```{r}

median_hs_prices_sub %>% 
  ggplot(aes(x = median_income, y = median_house_value))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)

```


Shortly we may try a regression model to fit the categorical predictor ocean_proximity. Investigate the level of ocean_proximity predictors. How many dummy variables do you expect to get from it?

5 variables

```{r}

unique(housing_prices$ocean_proximity)

```

Start with simple linear regression. Regress median_house_value on median_income and check the regression diagnostics.

```{r}

model <- lm(formula = median_house_value ~ median_income, data = housing_prices)

model

summary(model)
```

Add another predictor of your choice. Check your assumptions, diagnostics, and interpret the model.

```{r}

model_2 <- lm(formula = median_house_value ~ median_income + total_rooms, data = housing_prices)

summary(model_2)

```


