---
title: "Week 11 Logistic Regression Weekend Homework"
output:
  html_document:
    toc: yes
    toc_float: true
    theme: united

---
Kahlen Cheung
20/05/2022


```{r}
library(tidyverse)
library(janitor)
```


## Load in and clean data

```{r}

juice <- read_csv(here::here("data/orange_juice.csv")) %>% 
  clean_names() %>% 
  mutate(store7 = as.factor(store7)) %>% 
  mutate(purchase_mm = as.logical(recode(purchase,
                              "CH" = FALSE,
                              "MM" = TRUE)), .after = 1) %>% 
  mutate(weekof_purchase_level = case_when(
    weekof_purchase <= 243 ~ "low",
    weekof_purchase > 243 & weekof_purchase < 260 ~ "medium",
    weekof_purchase >= 260 ~ "high"), .after = 3) %>% 
  mutate(weekof_purchase_level = factor(weekof_purchase_level, levels = c("low", "medium", "high"))) %>% 
  select(-purchase, -weekof_purchase) %>% 
  na.omit()

view(juice)



```


## Observe potential predictors

```{r}

library(GGally)

alias(glm(purchase_mm ~., data = juice))

```

* Remove aliases variables  

```{r}
juice_trim <- juice %>% 
  select(-sale_price_ch, -sale_price_mm, -price_diff, -list_price_diff, -store )

view(juice_trim)
```


```{r}
ggpairs(juice_trim, c(1 : 7))
```



```{r}

ggpairs(juice_trim, c(1, 8:13))

```

* Examine multiple predictors  

```{r}

juice_logreg_model <- (glm(purchase_mm ~ ., data = juice_trim, family = binomial(link = "logit")))

juice_logreg_model_tidy <- broom::tidy(juice_logreg_model) %>% 
                                       
```

```{r}
format(8.997142e-3,scientific = FALSE)
```

The predictors below have the the significance at α=0.05, which means they are relatively relevant to the dependent variable `purchase_mm`. 

`price_ch`
`price_mm`
`disc_mm`
`loyal_ch`
`pct_disc_mm`

* Create models using the above predictors, and add predictions to them.

```{r}

library(modelr)

juice_price_model <- glm(purchase_mm ~ price_ch + price_mm,     #+ disc_mm + loyal_ch + pct_disc_mm,
                         data = juice_trim, 
                         family = binomial(link = "logit"))

juice_disc_model <-  glm(purchase_mm ~ price_ch + price_mm + disc_mm + pct_disc_mm,
                         data = juice_trim, 
                         family = binomial(link = "logit"))

juice_5pred_model <- glm(purchase_mm ~ price_ch + price_mm + disc_mm + loyal_ch + pct_disc_mm,
                         data = juice_trim, 
                         family = binomial(link = "logit"))

juice_price_model_ap <- juice_trim %>% 
  add_predictions(juice_price_model, type = "response")

juice_disc_model_ap <- juice_trim %>% 
  add_predictions(juice_disc_model, type = "response")

juice_5pred_model_ap <- juice_trim %>% 
  add_predictions(juice_5pred_model, type = "response")


juice_price_model_ap
juice_disc_model_ap
juice_5pred_model_ap

```

* create ROC

```{r}
library(pROC)

roc_obj_price <- juice_price_model_ap %>% 
  roc(response = purchase_mm, predictor = pred)

roc_curve_price <- ggroc(data = roc_obj_price, legacy.axes = TRUE)+
  coord_fixed()+
  ylab("sensitivity (TPR)")+
  xlab("1-specifity (TNR)")


```


```{r}

roc_obj_disc <- juice_disc_model_ap %>% 
  roc(response = purchase_mm, predictor = pred)

roc_curve_disc <- ggroc(data = roc_obj_disc, legacy.axes = TRUE)+
  coord_fixed()+
  ylab("sensitivity (TPR)")+
  xlab("1-specifity (TNR)")
```


```{r}
roc_obj_5pred <- juice_5pred_model_ap %>% 
  roc(response = purchase_mm, predictor = pred)

roc_curve_5pred <- ggroc(data = roc_obj_5pred, legacy.axes = TRUE)+
  coord_fixed()+
  ylab("sensitivity (TPR)")+
  xlab("1-specifity (TNR)")


```

```{r}

roc_curve_price 
roc_curve_disc
roc_curve_5pred 

```


* Calculate the AUC

```{r}
auc(roc_obj_price)

auc(roc_obj_disc)

auc(roc_obj_5pred)

```



## Cross Validation

```{r}
library(caret)

train_control <- trainControl(method = "repeatdcv",
                              number = 5,
                              repeats = 5000,
                              savePredictions = TRUE,
                              classProbs = TRUE,
                              summaryFunction = twoClassSummary)

# juice_trim_factor <- juice_trim %>% 
#   mutate(purchase_mm = if_else(purchase_mm == TRUE ,  "1" , "0" ))

train_model <- caret::train(as.factor(purchase_mm) ~ price_ch + price_mm + disc_mm + loyal_ch + pct_disc_mm,
                     data = juice_trim,
                     trControl = train_control,
                     method = "glm",
                     family = binomial(link = "logit"))

summary(train_model)

```


