---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggplot2)
library(CodeClanData)
library(janitor)
```

```{r}

qb_revenue_breakdown <- CodeClanData::qb_revenue_breakdown %>% 
  clean_names()
qb_monthly_sales <- CodeClanData::qb_monthly_sales %>% 
  clean_names()
qb_competitors <- CodeClanData::qb_competitors %>% 
  clean_names()
qb_device_data <- CodeClanData::qb_device_data %>% 
  clean_names()

view(qb_revenue_breakdown)

```


Question 1.
Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset. 
```{r}

ggplot(qb_revenue_breakdown, aes(x = year, y = revenue, fill = product))+
  geom_bar(position = "stack", stat="identity")

```

Question 2.
Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. This data is inside qb_monthly_sales, but you will need to use filter() or subset() (base R). 
```{r}

glimpse(qb_monthly_sales)

qb_monthly_sales_q2 <- filter(qb_monthly_sales, cashflow == "Kwikbit Unit 1 Sales") %>%
  arrange(date)

ggplot(qb_monthly_sales_q2, aes(x = date, y = amount))+
 geom_line()+
  xlab("\nDate")


```

Question 3.
Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.
```{r}

qb_monthly_sales_q3 <- qb_monthly_sales %>% 
  filter(cashflow != "Kwikbit Unit 1 Sales") %>%
  pivot_wider(names_from = cashflow,
              values_from = amount) %>% 
  clean_names() 

qb_monthly_sales_q3 <-qb_monthly_sales_q3 %>% 
  mutate(monthly_revenue = total_revenue-cost)


ggplot(qb_monthly_sales_q3, aes(x = date)) +
  geom_line( aes(y=total_revenue, colour = "total_revenue")) + 
  geom_line( aes(y=cost, colour = "cost"))+ylim(0,3000)+
  labs( x = "\nMothly Revenue",
        y = "Amount")

```


Question 4.
Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors. 
```{r}


# qb_competitors_q4 <- qb_competitors %>% 
#   pivot_wider(names_from = company,
#               values_from = revenue) %>% 
#   clean_names()
# 
# ggplot(qb_competitors_q4, aes( x = year, fill = revenue))+
# geom_area(stat ="bin", alpha=0.6) +
#   theme_classic()

```



