---
title: "Weekend_hm_model_building"
output:
  html_document:
    toc: yes
    toc_float: true
    theme: united

---

Kahlen Cheung
14/05/22

* Build a multiple linear regression model,  to model the `AveragePrice` of the avocados.  

* Use the validation techniques to evaluate the model.  

* Build an explanatory or a predictive model.  

* Interpreting the results and write in the scripts.  

```{r setup, message = FALSE, warning = FALSE}

library(tidyverse)
library(janitor)
library(GGally)
library(ggfortify)
library(modelr)
library(lubridate)

```


```{r echo=FALSE,results='hide'}

avocado <- read_csv(here::here("data/avocado.csv")) %>% 
  clean_names()

glimpse(avocado)
```


```{r}

avocado <- avocado %>% 
  mutate(month = month(date), .after = 13)

```


## Data Cleaning

Discard columns:
`x1` ( an index column), 
`date` (use year/month instead), 
`total_bags` ( It is computed from small/large/xlarge bags)
`region`

```{r}

avocado_trim <- avocado %>% 
  select(-x1, -date, -total_bags, -region)

```

* Add `month` column as one of the variables

```{r}

avocado_trim <- avocado_trim %>% 
  mutate(year = as.factor(year)) %>% 
  mutate(month = as.factor(month)) %>% 
  mutate(type = as.factor(type)) #

```

## Partitial dataset

### Use alias() to check whether the variables are unqiue to be predictors

1.1 Create a dataset that only contains numerical variables.

```{r}

avocado_null <- avocado_trim %>% 
  select(-year, -month, -type)

```

1.2 Check which variable is suitable to be the predictors

* no aliases in this dataset

```{r}

alias(lm(average_price ~ ., data = avocado_null))

```


2.1 Create a dataset that only contains categorical variables.

```{r}

avocado_cat <- avocado_trim %>% 
  select(average_price, year, month, type)

```

2.2 Check which variable is suitable to be the predictors

* no aliases in this dataset  

```{r}
alias(lm(average_price ~ ., data = avocado_cat))
```


## Find predictors

### Use ggpairs() to check corr values of predictors

* The corr value is <0 , which means there is negative association between `average_price` and all predictors

```{r}
ggpairs(avocado_null)
```

* The plot interprets an appropriate relations between `average_price` and all predictors: `year`, `month` and `type`. 

```{r}

ggpairs(avocado_cat)

```

## Bulding model

### Mod1a

average_price ~ year
r^2: 0.03489
p-value: < 2.2e-16

```{r}

mod1a <- lm(average_price ~ year, data = avocado_cat)

summary(mod1a)

```


```{r}

avocado_trim_resid <- avocado_cat %>% 
  add_residuals(mod1a) %>% 
  select(-c("average_price", "year"))

ggpairs(avocado_trim_resid)

```

### Mod1b

average_price ~ year + month
r^2: 0.09475
p-value: < 2.2e-16

```{r}

mod1b <- lm(average_price ~ year + month, data = avocado_cat)

summary(mod1b)

```

### Mod1c

average_price ~ year + month + type
r^2: 0.474
p-value: < 2.2e-16

```{r}

mod1c <- lm(average_price ~ year + month + type, data = avocado_cat)

summary(mod1c)

```

* `mod1c` has the greatest F value, means the group mean is highly relative to the variables. `modic` is the fittest model.

```{r}
anova(mod1a, mod1b, mod1c)
```


## Validation test

```{r}



```


